Visual Inference Test of the Hexagon Tile Map for Spatial Distributions

### 2021-01-11 supplementary/lineups.Rmd
darker figures

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r nwse-hex2, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 12 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_geo.png")))
```

@@

```{r nwse-hex3, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 3 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_geo.png")))
```

@@

```{r nwse-hex5, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 4 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_geo.png")))
```

@@

```{r nwse-hex6, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 9 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_6_geo.png")))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.path = "alldisplays/")
```

@@

```{r nwse-hex2, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 12 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_hex.png")))
```

@@

```{r nwse-hex3, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 3 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_hex.png")))
```

@@

```{r nwse-hex5, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 4 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_hex.png")))
```

@@

```{r nwse-hex6, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 9 contains a distribution that affects all capital nwse."}
ggdraw() +
  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_6_hex.png")))
```

### 2021-01-11 survey/survey.Rmd
darker figures

---
title: "Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference with crowdsourcing?"
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields
  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@qut.edu.au
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The abstract goes here.
  On multiple lines eventually.
dev: png
bibliography: mybibfile.bib
output: rticles::ieee_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE, 
  message = FALSE)
```

@@

@@

Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
The same data were shown on a choropleth map, and on a hexagon tile map.
Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.

Study Design
============

## Aims

This study aims to answer several questions around the presentation of spatial distributions:

1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?

2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
using a hexagon tile map display?
3. Do people find hexagon tile maps more difficult to read than choropleth maps?
4. Are the reasons for choosing a plot different depending on the type of display?
5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?

## Methodology

The online crowdsource platform Figure-Eight was used to recruit participants. 
A line up protocol was implemented to arrange 12 maps in each display. 
Individual displays were created by a combination of plot type, and spatial trend model.

The researchers contrasted the different plot designs, as hexagon tilemap
and geography in the lineups were created using the same data, and same null positions within the lineup.

## The participants

There were 95 participants in the study. 
We recruited participants using the Figure-Eight crowd source platform by advertising this survey to participants that fulfilled the following crtieria:

• level 2 or level 3 on the Figure-Eight Platform.
• at least 18 years old

Participants then selected our task from the list of tasks available to them.

## The variables being manipulated and measured?

The variables that were changed between groups were the type of plot shown and the trend model.

Each participant was randomly allocated to either group A or group B when they begun the survey. This resulted in 42 participants allocated to group A, and 53 participants allocated to group B.

Factor combinations examined by each participant amount to 6 (2x3) lineup displays.
A participant did see the same data for both plot types. Four simulated sets of data were generated for each treatment.
This will generate 24 lineups (12 were geographic maps, and 12 were hexagon tile maps). Participants will evaluate 12 lineups, 6 of each plot type. Appendix A shows the experimental design visually.
For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.

The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup. A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
High efficiency occurs when a small amount of time is taken to evaluate each lineup. This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.

## Participant training
Each participant saw three test displays orienting them to the task. Participants proceeded to the survey, this involved evaluating 12 displays.

## Experiment procudure and data collection
The participant submitted demographic questions and provided consent before evaluating the lineups.

Demographics were collected regarding the study participants:
• Gender (female / male / other),
• Degree education level achieved (high school / bachelors / masters / doctorate / other),
• Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
• Lived at least for one year in Australia (Yes / No )

Participants then moved to the evaulation phase.
The set of images differed for group A and group B.
After being allocated each individual was shown the 12 displays in randomised order.

Three questions were asked regarding each display:
- Plot choice
- Reason
- Difficulty

After completing the 12 evaluations, the participants were asked to submit their responses.

Data was collected through a web application containing the online survey.
Each participant used the internet to access the survey.

The data collection took place using a secure link between the survey web application and the googlesheet used to store results. The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.

## The methods of data analysis used
The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].

For each of the 12 lineup displays the researchers calculated:
• accuracy: the proportion of subjects who detected the data plot
• efficiency: average time taken to respond

### Visualisations
Side-by-side dot plots were made of accuracy (efficiency) against plot type, facetted by trend model type.

Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.

Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).

### Modeling

The results will be analysed using a generalised linear model, with a subject random effect. There will be two main effects: plot type and trend model, which gives the fixed effects part of the model to be

$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$

where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the plot type effect, $\delta_j$ is the trend model effect. We are allowing for an interaction between plot type and trend model. Because the response is binary, a logistic model is used.

A similar model will be constructed for the efficiency, using a log time, and normal errors.

The feedback and demographic variables will possibly be incorporated as covariates.

Computation will be done using R [@RCore], with the `lme4` package [@lme4].

## Limitations of the data collection

This required internet connection for participants to access the survey

Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991). All applicants provided informed consent in line with QUT regulations prior to participating in this research.

@@

```{r data}
###############################################################################

# Load Libraries
library(tidyverse)
library(lubridate)
library(broom)
library(readxl)
library(lme4)
library(ggthemes)

invthm <- theme(
  panel.background = element_rect(fill = "transparent", colour = NA), 
  plot.background = element_rect(fill = "transparent", colour = NA),
  legend.background = element_rect(fill = "transparent", colour = NA),
  legend.key = element_rect(fill = "transparent", colour = NA),
  text = element_text(colour = "white", size = 20),
  axis.text = element_text(colour = "white", size = 20)
)

# Downloaded data
d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))
```

@@

```{r}
##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")

@@

@@

#ggsave(filename = "figures/pilot/replicate_change_time.png", plot = repl_plot_t, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")

@@

@@

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix were assumed under latex,  -->
<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

>>>>

---
title: Visual Inference Test of the Hexagon Tile Map for Spatial Distributions
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields

  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@qut.edu.au
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The abstract goes here.
  On multiple lines eventually.

bibliography: mybibfile.bib
output: rticles::ieee_article
---

@@

Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
The same data will be shown on a choropleth map, and on a hexagon tile map.
Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.

Methodology
============

    Described the methods used to undertake the research including details of

This methodology section explains the various aspects of the research:

1. The overall structure of the research

The online crowdsource platform Figure-Eight was used to recruit participants.   
Each participant saw three test displays orienting them to the task.
They then took an online survey evaluating 12 displays.
A line up protocol was implemented to arrange 12 maps in each display. 
Individual displays were created by a combination of plot type, and spatial trend model.
The researchers contrasted the different plot designs, as hexagon tilemap
and geography in the lineups were created using the same data, and same null positions within the lineup.

2. The subject populations
<!-- The groups studied in the research including the size of each group and any features of the subjects which may be relevant to the topic being researched. -->

There were 95 participants in the study. Each participant was randomly allocated to either group A or group B when they begun the survey. This resulted in 42 participants allocated to group A, and 53 participants allocated to group B.

Demographics were collected regarding the study participants.

3. The variables being manipulated and measured?
    The variables that were changed between groups were the type of plot shown and the trend.
    The variables measured as a result of the changes were probability of detection and the time taken to submit responses.

Factor combinations to be examined by each participant amount to 6 (2x3) lineup displays.
A participant cannot see the same data for both plot types. Four simulated sets of data will be generated for each treatment.
This will generate 24 lineups (12 will be geographic maps, and 12 will be hexagon tile maps). Participants will evaluate 12 lineups, 6 of each plot type. Appendix A shows the experimental design visually.
For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.

4. The conditions under which the research was conducted?
Each participant used the internet to access the survey.
The participants determined the setting and time of day of the survey. There were many factors that could have determined the conditions under which the research was undertaken. Many factors or variations in conditions may have had an impact on the results.

5. The methods of data analysis used?
The data analysis methods used in order to analyse and collate the results were ...

6. Limitations of the data collection?
The data collection may have been influenced by several limitations.

Research Questions:
1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy
when viewed in a hexagon tile map display?
2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
using a hexagon tile map display?
3. Do people find hexagon tile maps more difficult to read than choropleth maps?
4. Are the reasons for choosing a plot different depending on the type of display?
5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?

For each plot evaluation the subject will provide these responses:
- Their choice of plot from a lineup
- Reason for choice of plot
- Time taken to respond
- Perceived difficulty in making a choice

@@

@@

```{r data}
###############################################################################
invthm <- theme(
  panel.background = element_rect(fill = "transparent", colour = NA), 
  plot.background = element_rect(fill = "transparent", colour = NA),
  legend.background = element_rect(fill = "transparent", colour = NA),
  legend.key = element_rect(fill = "transparent", colour = NA),
  text = element_text(colour = "white", size = 20),
  axis.text = element_text(colour = "white", size = 20)
)

# Load Libraries
library(tidyverse)
library(lubridate)
library(broom)
library(readxl)
library(lme4)
library(ggthemes)
# Downloaded data
d <- read_xlsx("../experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))
```

@@

```{r}
#ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
#ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")

@@

###########################################################

@@

ggsave(filename = "figures/pilot/replicate_change_time.png", plot = repl_plot_t, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
#ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")

@@

Here are two sample references: @Feynman1963118 [@Dirac1953888].

@@

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix will be assumed under latex,  -->
<!-- and a .pdf suffix will be assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

### 2021-01-11 survey/survey.tex
darker figures

@@

Experimental Design: Three trends were tested, in each of the two
displays. For each of the

Line up protocol:

\begin{itemize}
\item
  Experimental design

  \begin{itemize}
  \tightlist
  \item
    The overall structure and operation of the experiment or
    observational experience.
  \item
    The subject populations: The groups studied in the research
    including the size of each group and any features of the subjects
    which may be relevant to the topic being researched.
  \item
    The variables that were changed between groups and the variables
    measured as a result of the changes.
  \item
    The conditions under which the research was undertaken and any
    factors or variations in conditions which may have an impact on the
    results.
  \item
    The methods of data analysis used in order to analyse and collate
    the results.
  \item
    Any limitations of the data collected
  \end{itemize}
\end{itemize}

@@

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-SIEDAMD}{}%
Buja, Andreas, Dianne Cook, Heike Hofmann, Michael Lawrence, Eun-Kyung
Lee, Deborah F. Swayne, and Hadley Wlckham. 2009. ``Statistical
Inference for Exploratory Data Analysis and Model Diagnostics.''
\emph{Philosophical Transactions: Mathematical, Physical and Engineering
Sciences} 367 (1906): 4361--83.
\url{http://www.jstor.org/stable/40485732}.

>>>>

\begin{verbatim}
Described the methods used to undertake the research including details of 
\end{verbatim}

This methodology section explains the various aspects of the research:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The overall structure of the research
\end{enumerate}

@@

The online crowdsource platform Figure-Eight was used to recruit
participants.\\
Each participant saw three test displays orienting them to the task.
They then took an online survey evaluating 12 displays. A line up
protocol was implemented to arrange 12 maps in each display. Individual
displays were created by a combination of plot type, and spatial trend
model. The researchers contrasted the different plot designs, as hexagon
tilemap and geography in the lineups were created using the same data,
and same null positions within the lineup.

The researchers compared the length of time taken, and the accuracy of
the participants choices.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  The subject populations 
\end{enumerate}

There were 97 participants in the study. Each participant was randomly
allocated to either group A or group B when they begun the survey. This
resulted in 42 participants allocated to group A, and 53 participants
allocated to group B.

Demographics were collected regarding the study participants.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  The variables being manipulated and measured? The variables that were
  changed between groups were the type of plot shown and the trend. The
  variables measured as a result of the changes were probability of
  detection and the time taken to submit responses.
\end{enumerate}

The levels of the factors measured in the experiment were: • Plot type:
\emph{Geography, Hexagons} • Trend: \emph{Locations in two population
centres, Locations in multiple population centres, South-East to
North-West}

Factor combinations to be examined by each participant amount to 6 (2x3)
lineup displays. A participant cannot see the same data for both plot
types. Four simulated sets of data will be generated for each treatment.
This will generate 24 lineups (12 will be geographic maps, and 12 will
be hexagon tile maps). Participants will evaluate 12 lineups, 6 of each
plot type. Appendix A shows the experimental design visually.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\item
  The conditions under which the research was conducted? Each
  participant used the internet to access the survey. The participants
  determined the setting and time of day of the survey. There were many
  factors that could have determined the conditions under which the
  research was undertaken. Many factors or variations in conditions may
  have had an impact on the results.
\item
  The methods of data analysis used? The data analysis methods used in
  order to analyse and collate the results were \ldots{}
\item
  Limitations of the data collection? The data collection may have been
  influenced by several limitations.
\end{enumerate}

Research Questions: 1. Are spatial disease trends, that impact highly
populated small areas, detected with higher accuracy when viewed in a
hexagon tile map display? 2. Are people faster in detecting spatial
disease trends, that impact highly populated small areas, when using a
hexagon tile map display? 3. Do people find hexagon tile maps more
difficult to read than choropleth maps? 4. Are the reasons for choosing
a plot different depending on the type of display? 5. Does an Australian
resident find the choropleth map easier to read than the hexagon tile
map?

For each plot evaluation the subject will provide these responses: -
Their choice of plot from a lineup - Reason for choice of plot - Time
taken to respond - Perceived difficulty in making a choice

@@

The results section describes the findings of the research. When
outlining these findings, it is best to give the most central findings
first and then move on to the more peripheral results. For example, the
overall measure of learning would be given first and then the measures
of different types of learning.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-abs2016}{}%
``Australian Statistical Geography Standard (ASGS).'' 2018.
\emph{Australian Bureau of Statistics}. Australian Government.
\href{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)}{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian   Statistical Geography Standard (ASGS)}.

\leavevmode\hypertarget{ref-SIEDAMD}{}%
Buja, Andreas, Dianne Cook, Heike Hofmann, Michael Lawrence, Eun-Kyung
Lee, Deborah F. Swayne, and Hadley Wlckham. 2009. ``Statistical
Inference for Exploratory Data Analysis and Model Diagnostics.''
\emph{Philosophical Transactions: Mathematical, Physical and Engineering
Sciences} 367 (1906): 4361--83.
\url{http://www.jstor.org/stable/40485732}.
